%% Master CV - Kyle Bartlett
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs (cv/main_<company>.tex).
%%
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,letterpaper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Kyle Bartlett - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Kyle}{Bartlett}
\address{Crosby, TX (Greater Houston)}{}{}
\phone[mobile]{+1 765 427 2405}
\email{Kyle@BartlettLabs.io}
\extrainfo{\href{https://linkedin.com/in/kyle-bartlett}{LinkedIn}, \href{https://portfolio.bartlettlabs.io}{Portfolio}, \href{https://github.com/kyle-bartlett}{GitHub}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT  (tailor per role)
% ============================================================

\vspace{6pt}
\small{AI enablement leader who turns enterprise AI from pilot to platform. As US AI Lead at Anker I run AI adoption end to end -- assessing highest-impact use cases, building hands-on solutions on the modern LLM stack (Claude, OpenAI, agentic workflows), training people one-on-one, and tracking time saved, quality gains, and capability gaps -- and drove usage to \#1 of $\sim$200 employees company-wide. 15+ years bridging operations and applied AI (Apple, Anker), including leading a team of 10 and standing up an org-wide AI program. Founder of Bartlett Labs, shipping agentic AI applications on Claude/Anthropic APIs and Claude Code. I influence from the front line to the C-suite and make change stick.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{AI Enablement \& Adoption}: readiness assessments, adoption \& change management, one-on-one and team training, onboarding, internal community building, impact tracking.

\item \textbf{Agentic AI \& LLM Build}: agentic workflows, multi-agent orchestration, LLM APIs (Claude/Anthropic, OpenAI), RAG, vector DBs, prompt management \& output evaluation, Claude Code.

\item \textbf{Governance \& Impact}: AI governance, usage standards, data-quality guardrails, adoption \& impact reporting to executives.

\item \textbf{Engineering}: Python, TypeScript/JS, Next.js, React, Tailwind, SQL, Google Apps Script, Docker, Git, CI/CD, self-hosted infra (Coolify, Vultr), Vercel, AWS Bedrock.

\item \textbf{Operations \& Stakeholders}: demand forecasting, S\&OP, SAP, Tableau, dashboards \& metrics, executive communication.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

\item{\cventry{2026--Present}{US AI Lead}{Anker Innovations}{Remote, TX}{}{\vspace{1pt}
\begin{itemize}
    \item Own enterprise AI adoption across Anker's US org: readiness assessments, strategy, standards, and governance for safe AI use across a global US-China organization.
    \item Drove AI adoption to \textbf{\#1 of $\sim$200 employees} company-wide through hands-on one-on-one and small-group training.
    \item Architected a multi-agent AI platform (20+ autonomous jobs) and 10+ internal AI applications adopted across teams.
    \item Build, fine-tune, and evaluate a production LLM chatbot (weekly fine-tuning, RAG updates, prompt management, output evaluation).
\end{itemize}}}

\vspace{3pt}

\item{\cventry{2024--2026}{Demand Planner \& AI Automation Manager}{Anker Innovations}{Houston, TX}{}{\vspace{1pt}
\begin{itemize}
    \item Managed demand forecasting for Walmart ($\sim$50 SKUs), Costco, and Telecom accounts at >96.5\% in-stock as sole US ops member across a 14-hour timezone gap with China HQ.
    \item Built \textbf{300+ automation projects in 19 months}, incl. a 50+ script Google Apps Script platform (email ingestion -> validation -> exec dashboards) and an AI demand-forecasting model.
    \item Automated weekly executive reporting (Sunday ingest -> Tuesday reports), cutting hours to minutes with a data-validation layer catching errors pre-propagation.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{2025--Present}{Founder \& AI Automation Consultant}{Bartlett Labs}{Houston, TX}{}{\vspace{1pt}
\begin{itemize}
    \item Founded an AI automation consulting firm delivering production AI applications to SMBs, from discovery through deployment, training, and support.
    \item Built a 7-agent orchestration framework running 20+ autonomous cron jobs that shipped 226+ features; deployed 9+ live web apps on self-hosted infra with CI/CD.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{2019--2024}{Demand Planning Manager}{Apple, Inc.}{Austin, TX}{}{\vspace{1pt}
\begin{itemize}
    \item Led iPad supply chain across all retail stores and carriers; \textbf{100\% fill rate on 3 major product launches}.
    \item Presented 48-week rolling forecasts to C-Suite; managed 70+ vendor and internal relationships; mentored 5 contract hires.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{2015--2018}{Team Lead / Inventory Planning Manager}{Sears}{Hoffman Estates, IL}{}{\vspace{1pt}
\begin{itemize}
    \item Led a \textbf{team of 10} across \$120M receipts and \$52M sales at 99.95\% accuracy; ran an 18-month merger, trained 10+ analysts, consolidated 4 roles into 1.
\end{itemize}}}

\end{itemize}

% Earlier: Supply \& Demand Planner, Belk (2018--2019); Outside Sales, Spartan Energy (2019).

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{2008--2013}{BS, Engineering \& Industrial Management (GPA 3.5)}{Purdue University}{West Lafayette, IN}{}{\vspace{1pt}
Minors: Aeronautical Engineering, Science, Math, Technology.
}}

\vspace{3pt}

\item{\cventry{2016--2018}{Graduate business coursework (18 credits toward MBA)}{DePaul University}{Chicago, IL}{}{\vspace{1pt}
Business Administration, Management \& Operations.
}}

\end{itemize}

% ============================================================
%     CERTIFICATIONS & LANGUAGES
% ============================================================

\section{Certifications \& Languages}
\vspace{1pt}
\begin{itemize}
\item Microsoft Excel Masters Certification.
\item English (native).
\end{itemize}

% ============================================================
%     HONORS AND AWARDS
% ============================================================

\section{Honors and Awards}
\vspace{1pt}
\begin{itemize}
\item{\textbf{\#1 of $\sim$200 employees} -- Anker company-wide AI adoption leaderboard.}
\item{Former President -- BNI Houston Chapter.}
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
